Seminarium TI 3700\\ Data Analysis on Twitter(working title)

### 2014-03-23 authorinstr_2.tex
Hoofdlettergebruik tweet, twitter enzo aangepast
Hoofdlettergebruik tweet, twitter enzo aangepast nu wel

\begin{abstract}
Twitter is a popular microblogging website that allows users to share 140 character messages (tweets) with the rest of the world.
The analysis of such messages has become its own field within information technology, with a range of techniques that all share the same cause:
extracting useful information from these messages. This paper serves as an introduction to the research that has been done analysing tweets from Twitter,
covering the API and a series of common techniques. One of the key factors that contribute to succesful extraction is data enrichment, or somehow enhancing
the intended information from a tweet. This can be done by several techniques, yet this paper's scope limits to concept analysis and sentiment analysis.
When a stream of tweets is available for analysis, other techniques such as user classification, tag-based analysis and event identification offer valuable
insights into the behaviour of users on Twitter. All these techniques allow researchers to extract interesting information from Twitter activity, and allow
for a variety of applications to be created using this information.
\end{abstract}

@@

Microblogging has grown out to become one of the most interesting forms of social media. Its most popular implementation has to be Twitter, 
where users can share short messages, called tweets, with any other user. These short 140 character messages often contain valuable information about the user, their
interests, opinions, etc. This information can be very useful for a variety of applications, making social web data analytics an important field within
information technology. One of the biggest challenges is finding a way to extract the intended information from these tweets. 
This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics. 
We will build up from the basic techniques used by developers to collect tweets, to effective techniques that extract useful information from them. 
In the first following section the Twitter API will be evaluated, which will show that the platform offers useful tools and commands to retrieve 
specific datasets, or even a completely random sample stream of tweets. Once Twitter's API has been evaluated, a first series of techniques will be introduced
that focus on the analysis of a single tweet. These techniques offer insight in how machines and algorithms are being used to infer meaning from a tweet.
However, certain applications require the analysis of a set of tweets instead of just a single one. The final chapter is therefore dedicated to the explanation\
of common techniques used to retrieve information from multiple tweets. The conclusion of this paper involves a quick summary of the techniques that
have been reviewed throughout this paper.

@@

When the above fields are combined, it is possible to create datasets of Tweets that fulfill a certain specification. These sets can then be used to extract specific information. However, defining your own dataset may introduce a certain bias, and sometimes you need a random sample of tweets to analyze. For this purpose, Twitter has a streaming function that third party developers can tap into to retrieve random tweets. Unfortunately, the Twitter stream can only retrieve tweets that are less than a few days old.

@@

\subsubsection{Classification Features}
To classify users a set of features is needed to distinguish between users. In this section we will present a list of frequently used features to classify users.  
\\\\
\textbf{Linguistics}\\
Linguistics can say a lot about the interests of a user. Furthermore it can be used to distinguish between different types of users. One way to classify a user using linguistics is done by using Prototipical Words(PW's). \cite{userclasst} PW's are words that are more used by users in class $A$ than users in class $B$. (e.g. younger people will probably use terms like "lol" and "yolo" more than older users). To define prototipical words for i classes the propability that a user of class $c_i$ will use word $w$ needs to be calculated. Given n classes and some seed users $S_i$ this probability is calculated using the following formula: $proto(w, c_i) = \frac{|w, S_i|}{\sum_{j=1}^n |w, S_j|}$. \cite{userclasst} In a Twitter-context Prototipical Hashtags can be used in the same way.
\\\\
\textbf{Interaction Profiles}\\
Users interaction profiles is a profile created by Makazhanov \& Raﬁei to capture interactions between users and other accounts. \cite{pol} An interaction is a retweet or a reply. It is also possible to use friend accounts as a measurement in interaction between users.  A friend account of user $x$ is an account that is followed by user $y$. In the same way as prototypical words are calculated prototypical replies and retweets can be calculated to classify a user. (e.g. a democrat may tend to retweet a message from a democratic candidate) \cite{userclasst} 
\\\\  
\textbf{Tweeting Behavior}\\
Tweeting behavior is a set of characteristics which shows us the way a user interacts with Twitter. Features such as the average number of messages, the number of replies and the number of friends seems a good quantifier for classification. According to Pennacchiotti \& Popescu these features are useful but not really discriminative. \cite{userclasst} 
\\\\
\textbf{Profile}\\
Profile information can be helpful to classify a user, but it should be used with care due to the amount of fake, inconsistent or incorrect information. Research has shown that 80\% of the users provides a location and 48\% of the users provides a short bio. \cite{usermachine} It is was possible to extract a gender for 80\% of the users, but with a very low accuracy. They also researched the profile picture/avatar of twitter users and found out that these pictures can often be misleading. 20\% of the found profile pictures was not the owner but another person such as a celebrity. \cite{usermachine}

\subsubsection{Usecase: Predicting Political Preferences}
During election time it can be useful to predict the political preferences of a user. In Makazhanov \& Raﬁei's paper a solution to this problem is presented. As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets. \cite{pol} To achieve this (political) hashtags in combination with twitter activities is used. To know if a user mentions an account of an election candidate a number of these accounts are scraped semi-automaticall. This resulted in the collection of 181972 tweets about politics.\cite{pol}

@@

Event identification is the problem of identifying events(e.g. concerts, festivals and incidents) in a twitter-stream. The events identified range from Worldwide to local events. Twitter-messages related to an event can be a useful source of information as they often spread news earlier than the 'old' media (e.g News Papers and News Sites).

@@

\subsubsection{Event Identification Issues}
In this section we will discuss several issues regarding Event Identification and the solutions associated with them.
\\\\ 
\textbf{Separation of Event and Non-event Content}\\
Because not all tweets on twitter are event content, a separation of Event and Non-event content is done prior of identifying events. To achieve this separation, Becker et al.  use an incremental clustering algorithm(ICA). ICA doesn't require an number of clusters before the execution of the algorithm. This is an useful feature in the constantly changing twitter-environment. \cite{eventident}

@@

Then a labeling function is used to label the event, two types of labeling functions are tested. (1) Proximity-based Clustering (PbC) (2) Naive Bayes. PbC is an algorithm similar to K-means with k already known. The collection of tweets $X$ is observed and the class is returned for whicht the distance of between an event it's mean and the tweet vector is minimized. The Naive Bayes approach uses the formula $y = \arg\max_{y \in Y} P(y)\prod_i P(x_i, y)$ to assign the most probable class label $y \in Y$ to tweet $x$. The Naive Bayes approach outperforms PbC for all feature sets.  \cite{eventalign}
\subsubsection{Usecase: Earthquake Detection}
In Sakaki et al. their paper a usecase for Event Identification is presented in the form of a earthquake detection system. \cite{earthq} They consider twitter users as sensors. If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an earthquake is occurring.

To distinguish between tweets about Earthquakes a number of features is used. (1) The number of words in a tweet (2) The words in a tweet (3) Word context features. Feature (1) is a surprisingly good way to classify tweets about earthquakes, especially if it is used with a big amount of users. With the above feature set as basis, a system that detects earthquakes using twitter was built. After the system detects an earthquake an email to all users is sent. The system was used during 18. august - 2 September. In this time period 10 earthquakes had occurred, all of these earthquakes were detected. Furthermore Sakaki et al. their system detects an earthquake 10 minutes after happening and sends a message within a minute after detection. 
\cite{earthq}

>>>>

\begin{abstract}
Twitter is a popular microblogging website that allows users to share 140 character messages (tweets) with the rest of the world.
The analysis of such messages has become its own field within information technology, with a range of techniques that all share the same cause:
extracting useful information from these messages. This paper serves as an introduction to the research that has been done analysing tweets from Twitter,
covering the API and a series of common techniques. One of the key factors that contribute to successful extraction is data enrichment, or somehow enhancing
the intended information from a tweet. This can be done by several techniques, yet this paper's scope limits to concept analysis and sentiment analysis.
When a stream of tweets is available for analysis, other techniques such as user classification, tag-based analysis and event identification offer valuable
insights into the behaviour of users on Twitter. All these techniques allow researchers to extract interesting information from Twitter activity, and allow
for a variety of applications to be created using this information.
\end{abstract}

@@

Microblogging has grown out to become one of the most interesting forms of social media. Its most popular implementation has to be Twitter, 
where users can share short messages, called tweets, with any other user. These short 140 character messages often contain valuable information about the user, their
interests, opinions, etc. This information can be very useful for a variety of applications, making social web data analytics an important field within
information technology. One of the biggest challenges is finding a way to extract the intended information from these tweets.

This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics. 
We will build up from the basic techniques used by developers to collect tweets, to effective techniques that extract useful information from them. 
In the first following section the Twitter API will be evaluated, which will show that the platform offers useful tools and commands to retrieve 
specific datasets, or even a completely random sample stream of tweets. Once Twitter's API has been evaluated, a first series of techniques will be introduced
that focus on the analysis of a single tweet. These techniques offer insight in how machines and algorithms are being used to infer meaning from a tweet.
However, certain applications require the analysis of a set of tweets instead of just a single one. The final chapter is therefore dedicated to the explanation\
of common techniques used to retrieve information from multiple tweets. The conclusion of this paper involves a quick summary of the techniques that
have been reviewed throughout this paper.

@@

When the above fields are combined, it is possible to create datasets of tweets that fulfill a certain specification. These sets can then be used to extract specific information. However, defining your own dataset may introduce a certain bias, and sometimes you need a random sample of tweets to analyze. For this purpose, Twitter has a streaming function that third party developers can tap into to retrieve random tweets. Unfortunately, the Twitter stream can only retrieve tweets that are less than a few days old.

@@

\subsubsection{Classification Features}
To classify users a set of features is needed to distinguish between users. In this section we will present a list of frequently used features to classify users.  
\\\\
\textbf{Linguistics}\\
Linguistics can say a lot about the interests of a user. Furthermore it can be used to distinguish between different types of users. One way to classify a user using linguistics is done by using Prototipical Words(PW's). \cite{userclasst} PW's are words that are more used by users in class $A$ than users in class $B$. (e.g. younger people will probably use terms like "lol" and "yolo" more than older users). To define prototipical words for i classes the propability that a user of class $c_i$ will use word $w$ needs to be calculated. Given n classes and some seed users $S_i$ this probability is calculated using the following formula: $proto(w, c_i) = \frac{|w, S_i|}{\sum_{j=1}^n |w, S_j|}$. \cite{userclasst} In a Twitter-context Prototipical Hashtags can be used in the same way.
\\\\
\textbf{Interaction Profiles}\\
Users interaction profiles is a profile created by Makazhanov \& Raﬁei to capture interactions between users and other accounts. \cite{pol} An interaction is a retweet or a reply. It is also possible to use friend accounts as a measurement in interaction between users.  A friend account of user $x$ is an account that is followed by user $y$. In the same way as prototypical words are calculated prototypical replies and retweets can be calculated to classify a user. (e.g. a democrat may tend to retweet a message from a democratic candidate) \cite{userclasst} 
\\\\  
\textbf{Tweeting Behavior}\\
Tweeting behavior is a set of characteristics which shows us the way a user interacts with Twitter. Features such as the average number of messages, the number of replies and the number of friends seems a good quantifier for classification. According to Pennacchiotti \& Popescu these features are useful but not really discriminative. \cite{userclasst} 
\\\\
\textbf{Profile}\\
Profile information can be helpful to classify a user, but it should be used with care due to the amount of fake, inconsistent or incorrect information. Research has shown that 80\% of the users provides a location and 48\% of the users provides a short bio. \cite{usermachine} It is was possible to extract a gender for 80\% of the users, but with a very low accuracy. They also researched the profile picture/avatar of Twitter users and found out that these pictures can often be misleading. 20\% of the found profile pictures was not the owner but another person such as a celebrity. \cite{usermachine}

\subsubsection{Usecase: Predicting Political Preferences}
During election time it can be useful to predict the political preferences of a user. In Makazhanov \& Raﬁei's paper a solution to this problem is presented. As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets. \cite{pol} To achieve this (political) hashtags in combination with Twitter activities is used. To know if a user mentions an account of an election candidate a number of these accounts are scraped semi-automaticall. This resulted in the collection of 181972 tweets about politics.\cite{pol}

@@

Event identification is the problem of identifying events(e.g. concerts, festivals and incidents) in a Twitter-stream. The events identified range from Worldwide to local events. Twitter-messages related to an event can be a useful source of information as they often spread news earlier than the 'old' media (e.g News Papers and News Sites).

@@

\subsubsection{Event Identification Issues}
In this section we will discuss several issues regarding Event Identification and the solutions associated with them.
\\\\ 
\textbf{Separation of Event and Non-event Content}\\
Because not all tweets on Twitter are event content, a separation of Event and Non-event content is done prior of identifying events. To achieve this separation, Becker et al.  use an incremental clustering algorithm(ICA). ICA doesn't require an number of clusters before the execution of the algorithm. This is an useful feature in the constantly changing Twitter-environment. \cite{eventident}

@@

Then a labeling function is used to label the event, two types of labeling functions are tested. (1) Proximity-based Clustering (PbC) (2) Naive Bayes. PbC is an algorithm similar to K-means with k already known. The collection of tweets $X$ is observed and the class is returned for whicht the distance of between an event it's mean and the tweet vector is minimized. The Naive Bayes approach uses the formula $y = \arg\max_{y \in Y} P(y)\prod_i P(x_i, y)$ to assign the most probable class label $y \in Y$ to tweet $x$. The Naive Bayes approach outperforms PbC for all feature sets.  \cite{eventalign}
\subsubsection{Usecase: Earthquake Detection}
In Sakaki et al. their paper a usecase for Event Identification is presented in the form of a earthquake detection system. \cite{earthq} They consider Twitter users as sensors. If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an earthquake is occurring.

To distinguish between tweets about Earthquakes a number of features is used. (1) The number of words in a tweet (2) The words in a tweet (3) Word context features. Feature (1) is a surprisingly good way to classify tweets about earthquakes, especially if it is used with a big amount of users. With the above feature set as basis, a system that detects earthquakes using Twitter was built. After the system detects an earthquake an email to all users is sent. The system was used during 18. august - 2 September. In this time period 10 earthquakes had occurred, all of these earthquakes were detected. Furthermore Sakaki et al. their system detects an earthquake 10 minutes after happening and sends a message within a minute after detection. 
\cite{earthq}
